Technical Dimensions of Programming Systems

### 2022-05-31 prog-2022/prog22-master.tex
Start methodology Appendix + minor review changes
Perform appendectomy
Remove most material from body and reattach as appendix

% Class scrartcl Warning: seems someone has broken package `auxhook'.
% Usually this happens, if `auxhook' is loaded or used implicitly or explicitly
% by patching \document or via etoolbox command \AtEndPreamble. Trying an
% emergency workaround. You can avoid this warning adding:
\usepackage{auxhook}
% before \begin{document} on input line 6.
\usepackage{changepage} % For the single-page summary table PDF insert.
\usepackage{pdfpages}
\begin{document}

@@

%NOTE TO REVIEWERS: The main contribution of the paper is a comprehensive survey of 21 design dimensions of programming systems. Each one comes with detailed discussion, including known uses, to properly motivate it. We also elect to include the \emph{full set} of these dimensions in the main text. While these two aspects do make the paper longer than the recommended page limit, we prefer to err on this side than to privilege certain dimensions and relegate others to an appendix. We invite the reader to focus on the ones that best suit their interest.
\end{abstract}

@@

% \appendix
% \input{prog22-appendix.tex}

>>>>

% Class scrartcl Warning: seems someone has broken package `auxhook'.
% Usually this happens, if `auxhook' is loaded or used implicitly or explicitly
% by patching \document or via etoolbox command \AtEndPreamble. Trying an
% emergency workaround. You can avoid this warning adding:
\usepackage{auxhook}
% before \begin{document} on input line 6.
\usepackage{changepage} % For the single-page summary table PDF insert.
\usepackage{pdfpages}
\usepackage{pifont} % For checkmark / cross symbols for Appendix table :)

% Thanks https://tex.stackexchange.com/a/32687
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%

\begin{document}

@@

NOTE TO REVIEWERS: The main contribution of the paper is a comprehensive survey of 21 design dimensions of programming systems. Each one comes with detailed discussion, including known uses, to properly motivate it. Regrettably, we only have space for a small number of these dimensions in the main paper body. To give a broader picture of what we are contributing, we invite the reader to explore Appendix\ \ref{dimensions-catalogue} for dimensions that suit their interest.
\end{abstract}

@@

\appendix
\input{prog22-appendix.tex}
